\subsectiontitle{Master Students (\polimi)}

\begin{itemize}
    \item [ ] \ul{\it Filippo Bonfanti.}, co-supervised with Prof. Matteo Pelucchi and
          Prof. Marco Mehl. Present.

    \item [ ] \ul{\it Nicola Bernardi}, co-supervised with Prof. Alessandro Stagni.
          Present.

    \item [ ] \ul{\it Lorenzo Paggetta}, co-supervised with Prof. Alessandro Stagni.
          Thesis title: ``Simplified kinetic models for methane/air combustion''
          (\href{https://hdl.handle.net/10589/230242}{link}).

    \item [ ] \ul{\it Matteo Lea Casagrande}, co-supervised with Prof. Carlo Cavallotti,
          Prof. Matteo Pelucchi, Doct. Luna Pratali Maffei, Eng. Matteo Primi. Thesis title:
          ``Reconciling theory, experiments and gas-phase kinetic models. A case study on
          rigorous implementation of pressure dependent reactions in hydrogen combustion.''
          (\href{https://hdl.handle.net/10589/226533}{link}).

    \item [ ] \ul{\it Sara Meraviglia}, co-supervised with Prof. Matteo Pelucchi and Eng.
          Matteo Primi. Thesis title: ``Implementation of recent theoretical findings in
          hydrogen combustion model'' (\href{https://hdl.handle.net/10589/214934}{link}).

    \item [ ] \ul{\it Federico Marino}, co-supervised with Prof. Matteo Pelucchi. Thesis
          title: ``Automatic data management and model validation of ammonia-hydrogen and
          methane-hydrogen mixture combustion through the framework SciExpeM''
          (\href{https://hdl.handle.net/10589/212616}{link}).

    \item [ ] \ul{\it Amedeo Puri}, co-supervised with Prof. Alessandro Stagni and Eng.
          Alessandro Pegurri. Thesis title: ``Data-driven, class-based kinetic modeling of
          oxymethylene ethers combustion'' (\href{https://hdl.handle.net/10589/206686}{link}).

    \item [ ] \ul{\it Haithem Tej}, co-supervised with Prof. Matteo Pelucchi. Thesis title:
          ``Validation and optimization of a kinetic model for alcohols combustion using an
          automatic framework'' (\href{https://hdl.handle.net/10589/210401}{link}).

\end{itemize}
