\subsection{Conferences}
\begin{etaremune}
    \item
    47\textsuperscript{th} Meeting of the Italian Section of the Combustion Institute,
    Pisa, Italy. Oral contribution, ``{\it Beyond Conventional Models: Implementation of
    LMR-R Framework for Multi-Collider Systems in Hydrogen Combustion}''. {\bf
    Dinelli,~T.}, Primi,~M., Maffei,~L.P., Cuoci,~A., Cavallotti,~C., Pelucchi,~M.,
    % \hfill{}
    12-15~May~2025.

    \item
    12\textsuperscript{th} European Combustion Meeting, Edinburgh Scotland UK. Conference
    paper and poster presentation, ``{\it Reconciling theory, experiments and gas-phase
    kinetic models. A case study on rigorous implementation of pressure dependent
    reactions in hydrogen combustion.}''. {\bf Dinelli,~T.}, Primi,~M., Casagrande,~M.L.
    Maffei,~L.P., Cuoci,~A., Cavallotti,~C., Pelucchi,~M.,
    % \hfill{}
    07-10~April~2025.

    \item
    40\textsuperscript{th} International Symposium on Combustion, Milano Italy. Oral
    contribution based on the paper, ``{\it A data-driven, lumped kinetic modeling of
    OME\textsubscript{2-5} pyrolysis and oxidation}''. {\bf Dinelli,~T.},
    Pegurri,~A., Bertolino,~A., Parente,~A., Faravelli,~T., Mehl,~M, Stagni,~A.,
    % \hfill{}
    22-26~July~2024.

    \item
    19\textsuperscript{th} International Conference on Numerical Combustion, Kyoto
    Japan. Oral contribution, ``{\it Leveraging data assimilation techniques to
    integrate experimental and synthetic measurements in the kinetic mechanisms of
    e-fuels.}''. {\bf Dinelli,~T.}, Faravelli,~T., Stagni,~A., Ihme,~M.,
    % \hfill{}
    07-10~May~2024.

    \item
    Math2Product, Taormina, Italy. Oral contribution, ``{\it Comparative
    assessment of optimization algorithms for kinetic model optimization}''.
    {\bf Dinelli,~T.}, Stagni,~A.,
    % \hfill{}
    30~May-1~June~2023.

    \item
    45\textsuperscript{th} Meeting of the Italian Section of the Combustion Institute,
    Firenze, Italy. Oral contribution, ``{\it Automatic validation and optimization
    of a kinetic model for alcohols combustion}''. {\bf Dinelli,~T.},
    Pegurri,~A., Stagni,~A., Pelucchi,~M.,
    % \hfill{}
    28-31~May~2023.

    \item
    11\textsuperscript{th} European Combustion Meeting, Rouen, France. Conference paper
    and poster prsentation, ``{\it Developing a compact kinetic model for
    dimethoxymethane (DMM) combustion through a novel chemical lumping method}''.
    Pegurri, ~A., {\bf Dinelli,~T.}, Stagni,~A.,
    % \hfill{}
    26-28~April~2023.

    \item
    11\textsuperscript{th} European Combustion Meeting, Rouen, France. Conference paper
    and poster presentation, ``{\it Data-driven, class-based optimization methodology
    for the kinetic modeling of oxymethylene ethers (OME\textsubscript{1-4}) combustion}''.
    Puri,~A., {\bf Dinelli,~T.}, Pegurri, ~A., Stagni,~A.,
    % \hfill{}
    6-8~March~2023.

    \item
    AI4Energy (KAUST), Jeddah, Saudi Arabia. Poster presentation, ``{\it Data ecosystems for
    kinetic model reduction}''. {\bf Dinelli,~T.}, Ramalli,~E., Pegurri,
    ~A., Pernici,~B., Faravelli,~T., Stagni,~A.,
    % \hfill{}
    26-28~April~2023.

    \item
    18\textsuperscript{th} International Conference on Numerical Combustion, San Diego
    CA, USA. Oral contribution, ``{\it From detailed kinetics to large-scale
    simulations: integrating data ecosystems in the skeletal reduction framework}''.
    {\bf Dinelli,~T.}, Ramalli,~E., Pegurri,~A., Pernici,~B.,
    Faravelli,~T., Stagni,~A.,
    % \hfill{}
    08-11~May~2022.
    % Oral contribution within the mini symposium entitled: ``{\it From chemistry to turbulent
    %       combustion: Machine-learning tools for the integration of reduced-order models in
    %       reacting flow simulations}''.
\end{etaremune}

\subsection{Workshops}
\begin{etaremune}
    \item
    7\textsuperscript{th} International Workshop on Flame Chemistry, Milano, Italy.
    Poster presentation, ``{\it Assessment and Validation of recent theoretical
    findings in Hydrogen combustion kinetics: Master Equation and Mixture Rules}''.
    {\bf Dinelli,~T.}, Primi,~M., Pratali Maffei,~L., Cuoci,~A.,
    Cavallotti,~C., Pelucchi,~M.,
    % \hfill{}
    20-21~July~2024.
\end{etaremune}
