% !TEX encoding = UTF-8
% !TEX program = pdflatex
% !TEX spellcheck = en_GB

\documentclass[english,a4paper]{europasscv}
\usepackage[english]{babel}

\usepackage[backend=biber,autolang=hyphen,sorting=none,style=numeric,maxbibnames=99,doi=false,isbn=false,maxcitenames=2]{biblatex}
\usepackage{csquotes}
\usepackage{europasscv-bibliography}

\bibliography{bibliography}
\ecvbibhighlight{Dinelli}{Timoteo}{T.}

\ecvname{Timoteo Dinelli}
\ecvaddress{Piazza L. Da Vinci 32 Milano/Italy}
\ecvmobile{(+39) 348-3783020}
% \ecvtelephone{}
\ecvworkphone{(+39) 02-2399-3200}
\ecvemail{timoteo.dinelli@polimi.it timoteo.dinelli@gmail.com}
\ecvhomepage{https://tdinelli.github.io}
\ecvgithubpage{www.github.com/tdinelli}
% \ecvgitlabpage{www.gitlab.com/smith}
\ecvlinkedinpage{www.linkedin.com/in/timoteo-dinelli}
\ecvorcid[label, link]{0000-0003-1660-2965}
% \ecvim{AOL Messenger}{}
% \ecvim{Google Talk}{}

% \ecvgender{Male}
\ecvdateofbirth{13 July 1997}
\ecvnationality{Italian}

% \ecvpicture[width=3.8cm]{picture.jpg}

% \date{}

\begin{document}
   \begin{europasscv}

   \ecvpersonalinfo
   % \ecvbigitem{Job applied for}{European project manager}

   \ecvsection{Research Interest}

   \ecvitem{}{
      I'm a third-year Ph.D. student at Politecnico di Milano, affiliated with the Department of
      Chemistry, Materials, and Chemical Engineering Giulio Natta. I work within the CRECK
      modeling laboratory, under the supervision of Professor Alessandro Stagni. My Ph.D.
      research focuses on using data-driven methods to improve the development of chemical
      kinetics mechanisms for predicting combustion and pyrolysis behaviors of complex fuels.
      % My academic work revolves around several key areas:
      My academic pursuits revolve around several key areas of interest:

      \begin{ecvitemize}
         \item Setting up and managing an automated framework (SciExpeM) for systematically
            collecting and analyzing scientific data and kinetic
            models. \href{https://sciexpem.polimi.it}{Project link}.

         \item Developing robust pipelines to create and validate detailed kinetic mechanisms.
            These mechanisms are rigorously tested against extensive experimental datasets using
            data science methodologies.

         \item Creating automated routines to streamline the optimization of complex kinetic
            schemes, improving the efficiency of physics-based approaches.

         \item Implementing algorithms for conducting inverse modeling of high-dimensional
            problems, aiming to enhance predictive capabilities in complex systems.
      \end{ecvitemize}
   }

   \ecvsection{Work experience}

   \ecvtitle{October 2023 -- June 2024}{Visiting Ph.D. Student}
      \ecvitem{}{Stanford University, Stanford CA, USA.}
      \ecvitem{}{Visiting Ph.D. student at Stanford University’s FxLab, under the guidance
      of Professor Matthias Ihme. My research focuses on implementing Data Assimilation
      methods for the joint estimation of state and parameters within chemical kinetic
      dynamical systems.}

   \ecvsection{Education and training}

   \ecvtitlelevel{2021--present}{Ph.D. Chemical Engineering}{Politecnico~di~Milano}
      \ecvitem{}{Dissertation Advisor: Prof. Alessandro Stagni}
   \ecvtitlelevel{2019--2021}{Master of Sciece in Chemical Engineering}{Politecnico~di~Milano}
      \ecvitem{}{Thesis Title: Prof. ``\textit{Development of an automatic framework for
      kinetic model validation.}''.}
      \ecvitem{}{Thesis Advisors: Prof. Alessandro Stagni and Prof. Matteo Pelucchi.}
      % \ecvitem{}{Final Score: 107/110.}
   \ecvtitlelevel{2016--2019}{Bachelor of Science}{Politecnico~di~Milano}
      \ecvitem{}{Thesis Title: Prof. ``\textit{Applicazioni della stampa 3D per l’ingegnieria chimica.}''.}
      \ecvitem{}{Thesis Advisors: Prof. Giulia Luisa Bozzano.}
      % \ecvitem{}{Final Score: 96/110.}

   \pagebreak

   \ecvsection{Personal skills}
   \ecvmothertongue{Italian}
   \ecvlanguageheader
   \ecvlanguage{English}{C2}{C2}{C2}{C2}{C2}
   \ecvlanguagecertificate{Test of English for International Communication TOEIC (920/990)}
   \ecvlastlanguage{Spanish}{B1}{B1}{B1}{B1}{B1}
   \ecvlanguagefooter

   \ecvblueitem{Computer Skills}{
      \begin{ecvitemize}
         \item \textbf{Languages}: Proficient in C/C++, Python, Matlab. Experience in Fortran,
            Julia. Markup languages: \LaTeX, HTML, CSS, Markdown.

         \item \textbf{Software}: Most contributions can be found at \url{https://github.com/tdinelli}.
            During my PhD I have been, together with Edoardo Ramalli, the main developer
            and actual mantainer of the \href{https://sciexpem.polimi.it/}{SciExpeM}
            ecosystem, which involves and orchestrates different programs and software. I
            actively contributed to the development of
            \href{https://www.opensmokepp.polimi.it/}{OpenSMOKE++} ecosystem. My
            contributions include significant enhancements to the core library, as well as
            the development of functionalities for the ideal reactor and one-dimensional
            flame solvers, {\tt DoctorSMOKEpp}, and the creation of
            \href{https://github.com/burn-research/OptiSMOKE_toolbox}{OptiSMOKEpp}. I have
            developed a python interface,
            \href{https://github.com/tdinelli/OpenSMOKEpp_Interfaces}{OpenSMOKEpp\_Intrefaces},
            which exposes the key functionalities of the core {\tt OpenSMOKEpp} library.
            Additionally I have created comprehensive post-processing suite,
            \href{https://github.com/tdinelli/pySMOKEPostProcessor}{pySMOKEPostProcessor}.
            Presently, I am engaged in the development of the \texttt{CurveMatching}
            framework, which is tailored towards functional data analysis, with a specific
            emphasis on chemical kinetic data.
      \end{ecvitemize}


   }
   % \ecvblueitem{Organisational / managerial skills}{
   %    \begin{ecvitemize}
   %       \item whilst working for a Brussels based refugee NGO ``Convivial'' I organized a ``Civil Dialogue'' between refugees and civil servants at the European Commission 20th June 2002
   %       \item during my PhD I organised a seminar series on research methods
   %    \end{ecvitemize}
   % }
   %
   % \ecvdigitalcompetence{\ecvBasic}{\ecvIndependent}{\ecvProficient}{\ecvIndependent}{\ecvBasic}
   %
   % \ecvblueitem{Computer skills}{
   % \begin{ecvitemize}
   %    \item competent with most Microsoft Office programmes
   %    \item experience with HTML
   % \end{ecvitemize}
   % }
   %

   \ecvblueitem{Driving licence}{B}

   \nocite{*}
   \renewcommand{\section}[2]{\ecvsection{#2}}
   \printbibtabular[title=Publications]

\end{europasscv}
\end{document}
