\section{\sc Mentoring/ Supervision}

\textbf{Master Students} (Politecnico di Milano):

\begin{itemize}
    \item [ ] \textit{Lorenzo Paggetta}, co-supervised with Prof. Alessandro Stagni and Prof.
       Marco Mehl, Present.
    \item [ ] \textit{Matteo Lea Casagrande}, co-supervised with Prof. Matteo Pelucchi and Prof.
       Carlo Cavallotti, Present.
    \item [ ] \textit{Sara Meraviglia}, co supervised with Prof. Matteo Pelucchi and Eng. Matteo
       Primi. Thesis title: \textit{Implementation of recent theoretical findings in
       hydrogen combustion model} (\href{https://hdl.handle.net/10589/214934}{link}).
    \item [ ] \textit{Federico Marino}, co-supervised with Prof. Matteo Pelucchi. Thesis title:
       \textit{Automatic data management and model validation of ammonia-hydrogen and
       methane-hydrogen mixture combustion through the framework SciExpeM}
       (\href{https://hdl.handle.net/10589/212616}{link}).
    \item [ ] \textit{Amedeo Puri}, co-supervised with Prof. Alessandro Stagni and Eng.
       Alessandro Pegurri. Thesis title: \textit{Data-driven, class-based kinetic modeling
       of oxymethylene ethers combustion}
       (\href{https://hdl.handle.net/10589/206686}{link}).
    \item [ ] \textit{Haithem Tej}, co-supervised with Prof. Matteo Pelucchi. Thesis title:
       \textit{Validation and optimization of a kinetic model for alcohols combustion
       using an automatic framework} (\href{https://hdl.handle.net/10589/210401}{link}).
\end{itemize}
