% \section{\sc Invited Talks}
% \begin{etaremune}
% \end{etaremune}

\section{\sc Conferences and Presentations}
\begin{etaremune}
   \item
      Math2Product, Taormina, Italy. Oral contribution, ``\textit{Comparative
      assessment of optimization algorithms for kinetic model optimization}''.
      \textbf{\underline{Dinelli,~T.}}, Stagni,~A.,
      % \hfill{}
      30~May-1~June~2023.

   \item
      45\textsuperscript{th} Meeting of the Italian Section of the Combustion Institute,
      Firenze, Italy. Oral contribution, ``\textit{Automatic validation and optimization
      of a kinetic model for alcohols combustion}''. \textbf{\underline{Dinelli,~T.}},
      Pegurri,~A., Stagni,~A., Pelucchi,~M.,
      % \hfill{}
      28-31~May~2023.

   \item
      11\textsuperscript{th} European Combustion Meeting, Rouen, France. Conference paper
      and poster prsentation, ``\textit{Developing a compact kinetic model for
      dimethoxymethane (DMM) combustion through a novel chemical lumping method}''.
      Pegurri, ~A., \textbf{\underline{Dinelli,~T.}}, Stagni,~A.,
      % \hfill{}
      26-28~April~2023.

   \item
      11\textsuperscript{th} European Combustion Meeting, Rouen, France. Conference paper
      and poster presentation, ``\textit{Data-driven, class-based optimization methodology
      for the kinetic modeling of oxymethylene ethers (OME\textsubscript{1-4}) combustion}''.
      Puri,~A., \textbf{\underline{Dinelli,~T.}}, Pegurri, ~A., Stagni,~A.,
      % \hfill{}
      6-8~March~2023.

   \item
      AI4Energy (KAUST), Jeddah, Saudi Arabia. Poster presentation, ``\textit{Data ecosystems for
      kinetic model reduction}''. \textbf{\underline{Dinelli,~T.}}, Ramalli,~E., Pegurri,
      ~A., Pernici,~B., Faravelli,~T., Stagni,~A.,
      % \hfill{}
      26-28~April~2023.

   \item
      18\textsuperscript{th} International Conference on Numerical Combustion, San Diego
      CA, USA. Oral contribution, ``\textit{From detailed kinetics to large-scale
      simulations: integrating data ecosystems in the skeletal reduction framework}''.
      \textbf{\underline{Dinelli,~T.}}, Ramalli,~E., Pegurri,~A., Pernici,~B.,
      Faravelli,~T., Stagni,~A.,
      % \hfill{}
      08-11~May~2022.
      % Oral contribution within the mini symposium entitled: ``\textit{From chemistry to turbulent
      %       combustion: Machine-learning tools for the integration of reduced-order models in
      %       reacting flow simulations}''.
\end{etaremune}
